Miniproject - Analytic Number Theory

### 2021-11-30 Analytic number theory/submission.tex
added proof of dirichlets prime number theorem

\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{amsthm}
\usepackage[style=english]{csquotes}
\usepackage[language=english, backend=biber, style=alphabetic, sorting=nyt]{biblatex}

@@

\newtheorem{definition}{Definition}
\newtheorem{lemma}[definition]{Lemma}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{example}[definition]{Example}

\begin{document}
\maketitle

We use the convention that $\N = \{ n \in \Z \ | \ n \geq 0 \}$.

@@

    To show surjectivity, consider some Dirichlet character $f: \N \to \C$ and construct a group homomorphism $\chi: (\Z/q\Z)^\units \to \C^\units$. 
    For each $x \in (\Z/q\Z)^\units$, there is a representative $n \in \N$ of $x$ and as $f(n)$ does not depend on the choice of $n$, we may define $\chi(x) := f(n)$.
    Note that as $x \in (\Z/q\Z)^\units$, we find $n \perp q$ and so $f(n) \neq 0$, i.e. $f(n) \in \C^*$.
    Then clearly for $a, b \in (\Z/q\Z)^*$ with representatives $n, m \in \N$ have
    \begin{equation*}
        \chi(ab) = f(nm) = f(n)f(m) = \chi(a)\chi(b)
    \end{equation*}
    So $\chi$ is a well-defined group homomorphism and we obviously have $\tilde{\chi} = f$.
\end{proof}
\begin{example}[Part 1 (i)]
    \label{ex:nontrivial_dirichlet_character_mod_4}
    The function
    \begin{equation*}
        f: \N \to \C, \quad n \mapsto \begin{cases}
            0 & \text{if $n \equiv 0, 2 \mod 4$} \\
            1 & \text{if $n \equiv 1 \mod 4$} \\
            -1 & \text{if $n \equiv 3 \mod 4$}
        \end{cases}
    \end{equation*}
    is a Dirichlet character.
\end{example}
\begin{proof}
    This follows directly from Lemma~\ref{prop:characterization_dirichlet_character}, as $f = \tilde{\chi}$ for the group homomorphism
    \begin{equation*}
        \chi: (\Z/4\Z)^\units = \{ 1, 3 \} \to \C^*, \quad 1 \mapsto 1, \ 3 \mapsto -1
    \end{equation*}
    (this is a group homomorphism, as $3^2 = 9 \equiv 1 \mod 4$)
\end{proof}
Now we want to define Dirichlet series of Dirichlet characters.
\begin{proposition}
    For a Dirichlet character $\chi: \N \to \C$ and some $\epsilon > 0$, the series
    \begin{equation*}
        L(s, f) := \sum_{n \geq 1} f(n) n^{-s}
    \end{equation*}
    converges uniformly on $\Re(s) \geq 1 + \epsilon$.
    We will call it the Dirichlet series of $\chi$.
\end{proposition}
\begin{proof}
    By Lemma~\ref{prop:characterization_dirichlet_character}, we know that $\chi$ corresponds to a group homomorphism $\chi': (\Z/q\Z)^\units \to \C^\units$ such that $\chi(\N) = \chi((\Z/q\Z)^*) \cup \{ 0 \} \subseteq \C$ is a finite subset of $\C$.
    Hence, there is $C > 0$ with $|\chi(n)| \leq C$ for all $n \in \N$, and it follows that
    \begin{equation*}
        \sum_{1 \leq n \leq X} \left| f(n) n^{-s} \right| \leq \sum_{1 \leq n \leq X} C \left| n^{-s} \right| \leq C \sum_{1 \leq n \leq X} n^{-1 - \epsilon}
    \end{equation*}
    which is finite.
\end{proof}
\begin{proposition}[Part 1 (ii)]
    \label{prop:dirichlet_series_at_one}
    Let $\chi: (\Z/q\Z)^\units \to \C^\units$ be a group homomorphism. Then for the associated Dirichlet character $\tilde{\chi}$ we have that
    \begin{equation*}
        \lim_{s \to 1^+} L(s, \tilde{\chi}) \ \text{exists} \ \Leftrightarrow \ \sum_{x \in (\Z/q\Z)^\units} \chi(x) = 0
    \end{equation*}
    In this case, have that
    \begin{equation*}
        \lim_{s \to 1^+} L(s, \tilde{\chi}) = \sum_{n \geq 1} f(n) n^{-s}
    \end{equation*}
    where the right sum converges (but not absolutely) for $\Re(s) > 0$.
\end{proposition}
\begin{proof}
    Let $c = \sum_{x \in (\Z/q\Z)^\units} \chi(x)$.
    For the direction $\Rightarrow$ assume that $c \neq 0$.
    Then have for $\Re(s) > 1$ that
    \begin{align*}
        \sgn(c) \sum_{n \geq 1} \tilde{\chi}(n) n^{-s} &= \sum_{n \geq 1} \ \sum_{0 \leq k < q} \sgn(c) \tilde{\chi}(qn + k) (qn + k)^{-s} \\
        &\geq \sum_{n \geq 1} \ \sum_{0 \leq k < 1}\sgn(c) \tilde{\chi}(qn + k) (qn + n)^{-s} \\
        &= \sum_{n \geq 1} \sgn(c) (qn + n)^{-s} \underbrace{\sum_{0 \leq k < q} \tilde{\chi}(qn + k)}_{= c} \\
        &\geq \frac {|c|} {(q + 1)^s} \sum_{n \geq 1} n^{-s} = \frac {|c|} {(q + 1)^s} \zeta(s)
    \end{align*}
    which clearly has a pole at $s = 1$. Hence $\lim_{s \to 1^+} L(s, \tilde{\chi})$ cannot exist.

    For the other direction, assume that $c = 0$.
    Again, have for $\Re(s) > 1$ that
    \begin{align*}
        \sum_{n \geq 1} \tilde{\chi}(n) n^{-s} &= \sum_{n \geq 1} \ \sum_{0 \leq k < q} \tilde{\chi}(qn + k) (qn + k)^{-s} \\
        &= \sum_{n \geq 1} \ \sum_{0 \leq k < q} \tilde{\chi}(qn + k) \Bigl( (qn)^{-s} + (qn + k)^{-s} - (qn)^{-s} \Bigr)
    \end{align*}
    Observe that by Bernoulli's inequality, have
    \begin{align*}
        (qn)^{-s} - (qn + k)^{-s} &= \frac {(qn)^s - (qn + k)^s} {(q^2n^2 + qnk)^s} = (qn)^{s} \frac {1 - (1 + k(qn)^{-1})^s} {(q^2n^2 + qnk)^s} \\
        &\leq (qn)^s \frac {sk(qn)^{-1}} {(q^2n^2 + qnk)^s} = \frac {sk} {qn(qn + k)^s} = O(sn^{-s - 1})
    \end{align*}
    As $\chi((\Z/q\Z)^\units) \subseteq \C$ is finite, find $C > 0$ with $|\tilde{\chi}(n)| \leq C$ for all $n \in \N$. Then
    \begin{align*}
        \sum_{n \geq X} \tilde{\chi}(n) n^{-s} &= O(qCX^{-s}) + \sum_{n \geq X/q} \ \sum_{0 \leq k < q} \tilde{\chi}(qn + k) \Bigl( (qn)^{-s} + O(sn^{-s - 1}) \Bigr) \\
        &= O(qCX^{-s}) + \sum_{n \leq X/q} \Bigl( (qn)^{-s} c + \sum_{0 \geq k < q} O(Csn^{-s - 1}) \Bigr) = \\
        &= O(qCX^{-s}) + 0 + O\Bigl( Cqs \sum_{n \geq X/q} n^{-s - 1} \Bigr) \\
        &\leq O(qCX^{-s}) + O\Bigl( Cqs\zeta(s + 1) \Bigr)
    \end{align*}
    which is well-defined and finite for $\Re(s) > 0$.
    Further, the expression converges uniformly (as a function in $s$ on a neighborhood of $1$) to $0$ as $X \to \infty$. 
    So
    \begin{equation*}
        \sum_{n < X} \tilde{\chi}(n) n^{-s} \quad \text{converges uniformly to} \quad \sum_{n \geq 1} \tilde{\chi}(n) n^{-s}
    \end{equation*}
    as $X \to \infty$ (on a neighborhood of $1$). 
    Thus the limit is continuous and a continuation of $L(s, \tilde{\chi})$ which is defined on $\Re(s) > 1$.
    From this it follows that $\lim_{s \to 1} L(s, \tilde{\chi})$ exists and is equal to $\sum_n \tilde{\chi}(n) n^{-s}$.
\end{proof}
Applied to our example, we find
\begin{example}
    Let $f: \N \to \C$ be the Dirichlet character from Example~\ref{ex:nontrivial_dirichlet_character_mod_4} with corresponding group homomorphism $\chi: (\Z/4\Z)^\units \to \C$.
    Then
    \begin{equation*}
        \sum_{x \in (\Z/4\Z)^*} \chi(x) = \chi(1) + \chi(3) = 1 - 1 = 0
    \end{equation*}
    and so by Lemma~\ref{prop:dirichlet_series_at_one} the limit $\lim_{s \to 1^+} L(s, f)$ exists.
    The lemma further yields that
    \begin{align*}
        \lim_{s \to 1} L(s, f) &= \sum_{n \geq 1} f(n) n^{-1} = \sum_{n \geq 0} \frac {f(4n + 1)} {4n + 1} + \frac {f(4n + 3)} {4n + 3} = \sum_{n \geq 0} \frac 1 {4n + 1} - \frac 1 {4n + 3} \\
        &= 2 \sum_{n \geq 0} \frac 1 {(4n + 1)(4n + 3)} > 0
    \end{align*}
    is positive.
\end{example}

>>>>

\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{amsthm}
\usepackage[style=english]{csquotes}
\usepackage[language=english, backend=biber, style=alphabetic, sorting=nyt]{biblatex}

@@

\newtheorem{definition}{Definition}
\newtheorem{lemma}[definition]{Lemma}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{example}[definition]{Example}
\newtheorem{corollary}[definition]{Corollary}

\begin{document}
\maketitle
We use the convention that $\N = \{ n \in \Z \ | \ n \geq 0 \}$.
Further, we write $a \divides b$ if $a$ divides $b$ and $a \perp b$ if $a$ and $b$ are coprime.
Finally, let $\primes$ be the set of prime numbers in $\N$.

@@

    To show surjectivity, consider some Dirichlet character $f: \N \to \C$ and construct a group homomorphism $\chi: (\Z/q\Z)^\units \to \C^\units$. 
    For each $x \in (\Z/q\Z)^\units$, there is a representative $n \in \N$ of $x$ and as $f(n)$ does not depend on the choice of $n$, we may define $\chi(x) := f(n)$.
    Note that as $x \in (\Z/q\Z)^\units$, we find $n \perp q$ and so $f(n) \neq 0$, i.e. $f(n) \in \C^*$.
    Then clearly for $a, b \in (\Z/q\Z)^*$ with representatives $n, m \in \N$ have
    \begin{equation*}
        \chi(ab) = f(nm) = f(n)f(m) = \chi(a)\chi(b)
    \end{equation*}
    So $\chi$ is a well-defined group homomorphism and we obviously have $\tilde{\chi} = f$.
\end{proof}
\begin{example}[Part 1 (i)]
    \label{ex:nontrivial_dirichlet_character_mod_4}
    The function
    \begin{equation*}
        f: \N \to \C, \quad n \mapsto \begin{cases}
            0 & \text{if $n \equiv 0, 2 \mod 4$} \\
            1 & \text{if $n \equiv 1 \mod 4$} \\
            -1 & \text{if $n \equiv 3 \mod 4$}
        \end{cases}
    \end{equation*}
    is a Dirichlet character.
\end{example}
\begin{proof}
    This follows directly from Lemma~\ref{prop:characterization_dirichlet_character}, as $f = \tilde{\chi}$ for the group homomorphism
    \begin{equation*}
        \chi: (\Z/4\Z)^\units = \{ 1, 3 \} \to \C^*, \quad 1 \mapsto 1, \ 3 \mapsto -1
    \end{equation*}
    (this is a group homomorphism, as $3^2 = 9 \equiv 1 \mod 4$)
\end{proof}
Now we want to define Dirichlet series of Dirichlet characters.
\begin{proposition}
    For a Dirichlet character $\chi: \N \to \C$ and some $\epsilon > 0$, the series
    \begin{equation*}
        L(s, f) := \sum_{n \geq 1} f(n) n^{-s}
    \end{equation*}
    converges uniformly on $\Re(s) \geq 1 + \epsilon$.
    We will call it the Dirichlet series of $\chi$.
\end{proposition}
\begin{proof}
    By Lemma~\ref{prop:characterization_dirichlet_character}, we know that $\chi$ corresponds to a group homomorphism $\chi': (\Z/q\Z)^\units \to \C^\units$ such that $\chi(\N) = \chi((\Z/q\Z)^*) \cup \{ 0 \} \subseteq \C$ is a finite subset of $\C$.
    Hence, there is $C > 0$ with $|\chi(n)| \leq C$ for all $n \in \N$, and it follows that
    \begin{equation*}
        \sum_{1 \leq n \leq X} \left| f(n) n^{-s} \right| \leq \sum_{1 \leq n \leq X} C \left| n^{-s} \right| \leq C \sum_{1 \leq n \leq X} n^{-1 - \epsilon}
    \end{equation*}
    which is finite.
\end{proof}
\begin{proposition}
    \label{prop:dirichlet_series_at_one}
    Let $\chi: (\Z/q\Z)^\units \to \C^\units$ be a group homomorphism. Then for the associated Dirichlet character $\tilde{\chi}$ we have that
    \begin{equation*}
        \lim_{s \to 1^+} L(s, \tilde{\chi}) \ \text{exists} \ \Leftrightarrow \ \sum_{x \in (\Z/q\Z)^\units} \chi(x) = 0
    \end{equation*}
    In this case, have that
    \begin{equation*}
        \lim_{s \to 1^+} L(s, \tilde{\chi}) = \sum_{n \geq 1} f(n) n^{-s}
    \end{equation*}
    where the right sum converges (but not absolutely) for $\Re(s) > 0$.
\end{proposition}
\begin{proof}
    Let $c = \sum_{x \in (\Z/q\Z)^\units} \chi(x)$.
    For the direction $\Rightarrow$ assume that $c \neq 0$.
    Then have for $\Re(s) > 1$ that
    \begin{align*}
        \sgn(c) \sum_{n \geq 1} \tilde{\chi}(n) n^{-s} &= \sum_{n \geq 1} \ \sum_{0 \leq k < q} \sgn(c) \tilde{\chi}(qn + k) (qn + k)^{-s} \\
        &\geq \sum_{n \geq 1} \ \sum_{0 \leq k < 1}\sgn(c) \tilde{\chi}(qn + k) (qn + n)^{-s} \\
        &= \sum_{n \geq 1} \sgn(c) (qn + n)^{-s} \underbrace{\sum_{0 \leq k < q} \tilde{\chi}(qn + k)}_{= c} \\
        &\geq \frac {|c|} {(q + 1)^s} \sum_{n \geq 1} n^{-s} = \frac {|c|} {(q + 1)^s} \zeta(s)
    \end{align*}
    which clearly has a pole at $s = 1$. Hence $\lim_{s \to 1^+} L(s, \tilde{\chi})$ cannot exist.

    For the other direction, assume that $c = 0$.
    Again, have for $\Re(s) > 1$ that
    \begin{align*}
        \sum_{n \geq 1} \tilde{\chi}(n) n^{-s} &= \sum_{n \geq 1} \ \sum_{0 \leq k < q} \tilde{\chi}(qn + k) (qn + k)^{-s} \\
        &= \sum_{n \geq 1} \ \sum_{0 \leq k < q} \tilde{\chi}(qn + k) \Bigl( (qn)^{-s} + (qn + k)^{-s} - (qn)^{-s} \Bigr)
    \end{align*}
    Observe that by Bernoulli's inequality, have
    \begin{align*}
        (qn)^{-s} - (qn + k)^{-s} &= \frac {(qn)^s - (qn + k)^s} {(q^2n^2 + qnk)^s} = (qn)^{s} \frac {1 - (1 + k(qn)^{-1})^s} {(q^2n^2 + qnk)^s} \\
        &\leq (qn)^s \frac {sk(qn)^{-1}} {(q^2n^2 + qnk)^s} = \frac {sk} {qn(qn + k)^s} = O(sn^{-s - 1})
    \end{align*}
    As $\chi((\Z/q\Z)^\units) \subseteq \C$ is finite, find $C > 0$ with $|\tilde{\chi}(n)| \leq C$ for all $n \in \N$. Then
    \begin{align*}
        \sum_{n \geq X} \tilde{\chi}(n) n^{-s} &= O(qCX^{-s}) + \sum_{n \geq X/q} \ \sum_{0 \leq k < q} \tilde{\chi}(qn + k) \Bigl( (qn)^{-s} + O(sn^{-s - 1}) \Bigr) \\
        &= O(qCX^{-s}) + \sum_{n \leq X/q} \Bigl( (qn)^{-s} c + \sum_{0 \geq k < q} O(Csn^{-s - 1}) \Bigr) = \\
        &= O(qCX^{-s}) + 0 + O\Bigl( Cqs \sum_{n \geq X/q} n^{-s - 1} \Bigr) \\
        &\leq O(qCX^{-s}) + O\Bigl( Cqs\zeta(s + 1) \Bigr)
    \end{align*}
    which is well-defined and finite for $\Re(s) > 0$.
    Further, the expression converges uniformly (as a function in $s$ on a neighborhood of $1$) to $0$ as $X \to \infty$. 
    So
    \begin{equation*}
        \sum_{n < X} \tilde{\chi}(n) n^{-s} \quad \text{converges uniformly to} \quad \sum_{n \geq 1} \tilde{\chi}(n) n^{-s}
    \end{equation*}
    as $X \to \infty$ (on a neighborhood of $1$). 
    Thus the limit is continuous and a continuation of $L(s, \tilde{\chi})$ which is defined on $\Re(s) > 1$.
    From this it follows that $\lim_{s \to 1} L(s, \tilde{\chi})$ exists and is equal to $\sum_n \tilde{\chi}(n) n^{-s}$.
\end{proof}
Applied to our example, we find
\begin{example}[Part 1 (ii)]
    Let $f: \N \to \C$ be the Dirichlet character from Example~\ref{ex:nontrivial_dirichlet_character_mod_4} with corresponding group homomorphism $\chi: (\Z/4\Z)^\units \to \C$.
    Then
    \begin{equation*}
        \sum_{x \in (\Z/4\Z)^*} \chi(x) = \chi(1) + \chi(3) = 1 - 1 = 0
    \end{equation*}
    and so by Lemma~\ref{prop:dirichlet_series_at_one} the limit $\lim_{s \to 1^+} L(s, f)$ exists.
    The lemma further yields that
    \begin{align*}
        \lim_{s \to 1} L(s, f) &= \sum_{n \geq 1} f(n) n^{-1} = \sum_{n \geq 0} \frac {f(4n + 1)} {4n + 1} + \frac {f(4n + 3)} {4n + 3} = \sum_{n \geq 0} \frac 1 {4n + 1} - \frac 1 {4n + 3} \\
        &= 2 \sum_{n \geq 0} \frac 1 {(4n + 1)(4n + 3)} > 0
    \end{align*}
    is positive. 
    Wolfram Alpha \cite{wolfram_alpha} can give an explicit value to this sum, using the digamma function $\psi$. Namely
    \begin{equation*}
        \sum_{x \in (\Z/4\Z)^\units} f(n) n^{-1} = \frac 1 4 (\psi(\frac 7 4) - \psi(\frac 5 4))
    \end{equation*}
    which seems to be $\frac 1 4$.
\end{example}
Now we want to study the series
\begin{equation*}
    \sum_p f(p) p^{-s}
\end{equation*}
For this, we are first interested in how many primes $\equiv 1, 3 \mod 4$ there are.
\begin{lemma}
    \label{prop:prime_factor_3_mod_4}
    Let $n \equiv 3 \mod 4$. Then $n$ has a prime factor $p \equiv 3 \mod 4$.
\end{lemma}
\begin{proof}
    Use induction on $n$.
    If $n = 3$, the claim is trivial. 
    So let $n > 3$. If $n$ is prime, the claim again follows.
    Otherwise, have $n = ab$ with nontrivial divisors $a, b$.
    However, $3 \equiv n$ is not a square modulo $4$, so find that $a \not\equiv b \mod 4$.
    As both $a$ and $b$ must be odd, we see that either $a \equiv 3 \mod 4$ or $b \equiv 3 \mod 4$ and the claim follows by the induction hypothesis.
\end{proof}
\begin{corollary}[Part 1 (iii)]
    There are infinitely many primes $p$ with $p \equiv 3 \mod 4$.
\end{corollary}
\begin{proof}
    It suffices to show that there is a prime number $q \equiv 3 \mod 4$ with $q \geq N$ for every $N \in \N$.
    Let
    \begin{equation*}
        P := \prod_{p \in \primes, \ p \leq N} p
    \end{equation*}
\end{proof}
For the case of primes $\equiv 1 \mod 4$, I have remembered the two-square theorem and its connection to primes in the ring $\Z[i]$ of Gaussian integers, and somehow my train of thoughts went into Algebraic Number Theory.
After some research, I have found an exercise in \cite[Chapter I, §10]{neukirch} that requires the reader to prove the following proposition.
\begin{proposition}
    Let $q \geq 3$ be an integer.
    Then there are infinitely many primes $p$ with $p \equiv 1 \mod q$.
\end{proposition}
\begin{proof}
    Assume there were only finitely many such primes $p_i$, then we have their product $P = \prod_i p_i \in \Z$.
    Consider now the $q$-th cyclotomic polynomial $\Phi_q$.
    Clearly $\Phi_q(qPX) - 1 \in \Q[X]$ has at most $\phi(q)$ zeros, so there exists some $x \in \Z$ with $\Phi_q(qPx) \neq 1$ (this ``Ansatz'' was given as a hint).

    Let now $K = \Q(\omega_q)$ be the $q$-th cyclotomic number field with a primitive $q$-th root of unity $\omega_q$ (i.e. $\Phi_q(\omega_q) = 0$).
    Let further $\mathcal{O} \subseteq K$ be the ring of integral elements over $\Z$ in $K$.
    The prime decomposition law for Dedekind ring extension \cite[Chapter I, Prop 8.3]{neukirch} tells us that for a prime $p$, the ideal $(p)$ is reducible in $\mathcal{O}$ if and only if $\Phi_q \mod p$ is reducible.
    As $(\Z/p\Z)^\units$ is cyclic of order $p - 1$, this is the case if and only if $q \divides p - 1$, i.e. $p \equiv 1 \mod q$.

    Now consider the element $\alpha = \omega_q - xqP \in \mathcal{O}$. Then
    \begin{align*}
        N_{K/\Q}(\alpha) &= \prod_{\sigma: K \to \C \ \text{$\Q$-field homomorphism}} \sigma(\omega_q - xqP) \\
        &= \prod_{\sigma} (\sigma(\omega_q) - xqP) = \mathrm{MiPo}_\Q(\omega_q)(xqP) = \Phi_q(xqP) \neq 1
    \end{align*}
    as $\mathrm{MiPo}_\Q(\omega_q) = \prod_\sigma (\sigma(\omega_q) - X)$.
    Hence, $\alpha$ is not a unit in $\mathcal{O}$.
    On the other hand, $(\alpha)$ is coprime to $(p_i)$ for each $p_i$, as 
    \begin{equation*}
        \omega_q = \alpha - xqP \in (\alpha) + (p_i) \quad \text{and} \quad \omega_q \in \mathcal{O}^\units
    \end{equation*}
    By our assumption, the only prime ideals in $\mathcal{O}$ are the prime ideal factors of $(p_i)$ and $(p)$ for $p \neq p_i$.
    Thus, the prime ideal factorization of $(\alpha)$ consists only of prime ideals $(p), p \neq p_i$ and it follows that $(\alpha) = (n)$ for some integer $n \geq 2$.
    As $\omega_q$ and $xqP \in \Z$ are $\Q$-linearly independent, we see that $n \divides \omega_q$ and $n \divides xqP$.
    However, the former is a contradiction, as $\omega_q \in \mathcal{O}^\units$ is a unit and no $n \geq 2$ is a unit.
\end{proof}
The book also mentions that the general case can be proven by using L-series in algebraic number fields.
\begin{corollary}[Part 1 (iii)]
    There are infinitely many primes $p$ with $p \equiv 1 \mod 4$.
\end{corollary}
